---
main_topsize: 0.4 #percent coverage of the poster
main_bottomsize: 0 #https://github.com/brentthorne/posterdown/wiki/posterdown_html
main_width: 1
main_fontfamily: xaringanthemer::google_font('Baloo Bhai 2')
font_family: "Roboto"
column_margins:	"0.15in"
titlebox_height: "5%" #https://github.com/brentthorne/posterdown/issues/113  The default is "15%"
title_textsize: "50pt" #poster title fontsize
primary_colour:  "#21177A60" #mas 2 digitos para la trasparencia
secondary_colour: "#ff7f50"
author_textcol:  "#ed4a11" # "#bf846f" #Colour of author text.
author_textsize: "40pt"
poster_height: "40in"
poster_width: "42in"
accent_colour: "#aaaaaa"
affiliation_textcol: "#bf846f" # "#591F0A"
affiliation_textsize: "35pt"
font_size: 90%
#ESSENTIALS
sectitle_textsize: "40pt"
sectitle2_textsize: "30pt"
#sectitle_boxshape: "3mm 0mm" #Changes the shape of the section title box.
title: '**Assessing the impact of substance use treatment for preventing criminal justice system contact in Chile**'
author:
  - name: '**M. Mateo Piñones**'
    affil: 1, 2
    main: true
    orcid: '0000-0002-9607-7541'
    email: mariel.mateopinones@griffithuni.edu.au
  - name: '**A. González-Santa Cruz**'
    affil: 1, 3
    main: true
    orcid: '0000-0002-5166-9121'    
    email: gonzalez.santacruz.andres@gmail.com
  - name: '**A. Castillo-Carniglia**'
    affil: 4, 5
    main: true
    orcid: '0000-0002-3016-890X'    
    email: alvacasti@gmail.com
affiliation:
  - num: 1
    address: Young Researcher, Millennium Nucleus for the evaluation and analysis of Drug Policies 
  - num: 2
    address: Ph.D. student, School of Public Health, Universidad de Chile
  - num: 3
    address: Ph.D. student, Griffith University, Australia
  - num: 4
    address: Director , Millennium Nucleus for the evaluation and analysis of Drug Policies
  - num: 5
    address: Associate Professor, Society & Health Research Center
main_findings: none #- "**Baseline Treatment Completion** is associated with **lower hazards** of experiencing posterior contacts with justice system that ended in a **sentence or imprisonment**."
logoleft_name: _style/Logo_nDP_monotono_vertical_en.png
logoright_name: _style/Logo_nDP_color_hz_en.png
logocenter_name: _figs/qrcode.png #"`r plot(qrcode::qr_code('https://fondecytacc.github.io/nDP/'))`"
output: 
  posterdown::posterdown_html:
    self_contained: true
    pandoc_args: --mathjax
    number_sections: false
    css: xaringan-themer.css
    csl: ./_bibs/revista-medica-de-chile #american-medical-association-10th-edition.csl
knit: pagedown::chrome_print
---

<!---
knit: pagedown::chrome_print    
#https://github.com/brentthorne/posterdown/wiki/posterdown_betterport
#despues de number_section
#knit: pagedown::chrome_print
#https://docs.google.com/document/d/1O9_FGXL4jDPn19yp4Pb6y0w0BZtbocMK90ee8Gz3FNg/edit#
#bibliography: ./_bibs/libreria_generica.bib
#link-citations: true

https://github.com/brentthorne/posterdown/wiki/posterdown_html
--->

```{css, echo=FALSE}
div.title_container{
   background-image: linear-gradient(#ff7f50 10%, #21177A); /* background-color: #21177A;*/
}

div.logo_left{
  background-image: linear-gradient(#ff7f50 10%, #21177A);/* background-color: #ff7f50; */
}
div.logo_right{
  background-image: linear-gradient(#ff7f50 10%, #21177A); /*background-color: #ff7f50; */
}

:root {
  --text-bold-color: #21177A;
}

/* gray #4a4a4a */
```

```{=html}
<style type="text/css">
.showopt {   
  background-color: #004c93;   color: #FFFFFF;    width: 100px;   height: 20px;   text-align: center;   vertical-align: middle !important;   float: right;   font-family: sans-serif;   border-radius: 8px; 
  }

.showopt:hover {     
        background-color: #dfe4f2;
        color: #004c93; 
        }  
pre.plot {   
        background-color: white !important; 
        } 
.tablelines table, .tablelines td, .tablelines th {
        border: 1px solid black;
        }

.centrado {
    text-align: center;
}

.table.center {
    margin-left:auto; 
    margin-right:auto;
  }

/* https://vivekjaiskumar.medium.com/css-is-and-not-selector-17c942ec83f :is()*/

/* Applies to outputs that are not code other than R*/

pre {
  overflow-x: auto !important;
}
pre code {
  word-wrap: normal !important;
  white-space: pre !important;
}
/*
pre:not(.sourceCode) { 
  white-space: nowrap !important;
}
*/
.sourceCode { /* Important gives precedence  */
  font-size: 10px !important;
  line-height: 50% !important;
}

.text_35 { /* Important gives precedence  */
  font-size: 35% !important;
}

.text_38 { /* Important gives precedence  */
  font-size: 38% !important;
}

.text_40 { /* Important gives precedence  */
  font-size: 40% !important;
}

.text_45 { /* Important gives precedence  */
  font-size: 45% !important;
}

.text_50 { /* Important gives precedence  */
  font-size: 50% !important;
}

.text_55 { /* Important gives precedence  */
  font-size: 55% !important;
}

.text_60 { /* Important gives precedence  */
  font-size: 60% !important;
}

.text_65 { /* Important gives precedence  */
  font-size: 65% !important;
}

.text_70 { /* Important gives precedence  */
  font-size: 70% !important;
}

.text_75 { /* Important gives precedence  */
  font-size: 75% !important;
}

body{ /* Normal  */
      text-align: justify;
  }

.superbigimage{
    overflow-y:scroll;
    height:350px;
    white-space: nowrap;
    overflow-x: auto; 
    width:100%;
}
.superbigimage img{
    overflow-y: scroll;
    overflow-x: hidden;
}

.message { color:#446C6E; font-family: monospace;font-size: 10px; line-height: 110%; font-weight: bold;}
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 5px; text-align: justify;}
div.red { background-color:#e6bab1; border-radius: 5px; padding: 5px; text-align: justify;}

.pandoc-table { /* Should add !important; but it seems no necessary  */
  margin-left:auto; /* To center */
  margin-right:auto;
  border-collapse: collapse;
  table-layout: auto;
  font-size: 7px;
  overflow-y: auto;
  max-height:450px !important;
  white-space: nowrap;
  overflow-x: auto; 
  width:450px;
}

.pandoc-table th {/* header */
text-align: center !important;
font-size: 7px;
padding: 0px;
}

.pandoc-table td {
text-align: left !important;
font-size: 6px;
padding: 0px;
}

.pandoc-table caption {
    text-align: left !important;
    font-size: 11px !important;
}

.controlly{
    overflow-y:scroll;
    height:350px;
    overflow-x: scroll; 
}

.text_50_bib { /* Important gives precedence  */
  font-size: 50% !important;
  line-height: .9em !important;
}

ule {
  font-size: 55% !important;
  line-height: 1.1em !important;
  display: grid !important;
  grid-template-columns: repeat(2, 1fr) !important;
}

</style>

<style>
p.caption {
 margin-top: 0;
 margin-bottom: 0;
}
</style>

<style>
.showopt {
  background-color: #004c93;
  color: #FFFFFF; 
  width: 100px;
  height: 20px;
  text-align: center;
  vertical-align: middle !important;
  float: right;
  font-family: sans-serif;
  border-radius: 8px;
}

.showopt:hover {
    background-color: #dfe4f2;
    color: #004c93;
}

pre.plot {
  background-color: white !important;
}
</style>
```

```{js hideOutput, echo=F}
$(document).ready(function() {    
	$chunks = $('.fold');    
	$chunks.each(function () {      // add button to source code chunks     
	if ( $(this).hasClass('s') ) {       
		$('pre.r', this).prepend("<div class=\"showopt\">Show Source</div><br style=\"line-height:22px;\"/>");
       		$('pre.r', this).children('code').attr('class', 'folded');     
       		}      // add button to output chunks     
		if ( $(this).hasClass('o') ) {       
			$('pre:not(.r)', this).has('code').prepend("<div class=\"showopt\">Show Output</div><br style=\"line-height:22px;\"/>");       
			$('pre:not(.r)', this).children('code:not(r)').addClass('folded');        // add button to plots       
			$(this).find('img').wrap('<pre class=\"plot\"></pre>');       
			$('pre.plot', this).prepend("<div class=\"showopt\">Show Plot</div><br style=\"line-height:22px;\"/>");       
			$('pre.plot', this).children('img').addClass('folded');      
			}   
});    // hide all chunks when document is loaded   
	$('.folded').css('display', 'none')    // function to toggle the visibility   
	$('.showopt').click(function() {     
			var label = $(this).html();     
			if (label.indexOf("Show") >= 0) {       
				$(this).html(label.replace("Show", "Hide"));     
			} else {
			  $(this).html(label.replace("Hide", "Show"));     
			}     
	$(this).siblings('code, img').slideToggle('fast', 'swing');   
	}); 
}); 
```


```{r prev-setup, include = FALSE, cache=T, error=T}
rm(list=ls());gc()

#If you render multiple documents from the same script or R session, you should detach("Statamarkdown") in between documents.
try(detach("Statamarkdown"))

if(!grepl("4.1.2",R.version.string)){stop("Different version (must be 4.1.2)")}
path<-getwd()#we define it again later in setup chunk
if (grepl("CISS Fondecyt",path)==T){
    try(setwd("C:/Users/CISS Fondecyt/Mi unidad/Alvacast/SISTRAT 2022 (github)"));load("C:/Users/CISS Fondecyt/Mi unidad/Alvacast/SISTRAT 2022 (github)/15.Rdata")
  } else if (grepl("andre",path)==T){
    try(setwd('C:/Users/andre/Desktop/SUD_CL/'));load("E:/Mi unidad/Alvacast/SISTRAT 2022 (github)/15.Rdata")
  } else if (grepl("E:",path)==T){
    try(setwd("E:/Mi unidad/Alvacast/SISTRAT 2022 (github)/SUD_CL/"));load("E:/Mi unidad/Alvacast/SISTRAT 2022 (github)/15.Rdata")
  } else {
    try(setwd(paste0(path)));load(paste0(gsub("SUD_CL","",gsub("2022","2019",path)),"/15.Rdata"))
  }


```


```{r setup, include = FALSE, cache=T, error=T, echo=T}
#Libraries used in the routine. Dont change the order
local({r <- getOption("repos")
       r["CRAN"] <- "http://cran.r-project.org" 
       options(repos=r)
})
copiar_nombres <- function(x,row.names=FALSE,col.names=TRUE,dec=",",...) {
  if(class(try(dplyr::ungroup(x)))[1]=="tbl_df"){
        if(options()$OutDec=="."){
            options(OutDec = dec)
            write.table(format(data.frame(x)),"clipboard",sep="\t",row.names=FALSE,col.names=col.names,...)
            options(OutDec = ".")
          return(x)
        } else {
            options(OutDec = ",")
            write.table(format(data.frame(x)),"clipboard",sep="\t",row.names=FALSE,col.names=col.names,...)
            options(OutDec = ",")
          return(x)    
        }
  } else {
        if(options()$OutDec=="."){
            options(OutDec = dec)
            write.table(format(x),"clipboard",sep="\t",row.names=FALSE,col.names=col.names,...)
            options(OutDec = ".")
          return(x)
        } else {
            options(OutDec = ",")
            write.table(format(x),"clipboard",sep="\t",row.names=FALSE,col.names=col.names,...)
            options(OutDec = ",")
          return(x)       
  }
 }
}  
pacman::p_unlock(lib.loc = .libPaths()) #para no tener problemas reinstalando paquetes

if(!require(pacman)){install.packages("pacman")}
if(!require(devtools)){install.packages("devtools", type = "win.binary", dependencies=T)}

pacman::p_load(APCtools, ggpattern, withr, boot, matrixStats, knitr, tidyr, stringi,stringr, ggplot2, Hmisc, kableExtra, plotly, janitor, rbokeh, zoo, broom, sqldf, devtools, codebook, data.table, panelr, RColorBrewer, lsmeans, finalfit, ggiraph, sf, treemapify, dplyr, tidyverse, epiR, survminer, survival, ggfortify, survMisc, foreign, reshape2, stargazer, tableone, MatchIt, cobalt, eha, igraph, Amelia, DiagrammeR, DiagrammeRsvg, rsvg, mstate, htmltools, webshot, flexsurv, muhaz, Metrics, rpivotTable, caret, polycor, ClusterR, flextable, ggstatsplot, ggside, daff, explore, sjPlot, compareGroups, job, missForest, showtext, ggpattern, distill, showtext, googleVis, tidylog, magick, dlookr, easystats, tidylog, sqldf,  adjustedCurves, ggpmisc, rms, rateratio.test, XML, RCurl, rlist, install=T)


#Error in if (options$noisey == TRUE) message(paste("\n", options$engine, : argument is of length zero


if(!require(survcomp)){try(devtools::install_github("bhklab/survcomp",upgrade ="never"))}

try(webshot::install_phantomjs())

if(!require(bpmn)){try(devtools::install_github("bergant/bpmn",upgrade ="never"))}

#if(!require(Statamarkdown)){try(devtools::install_github("Hemken/Statamarkdown",upgrade ="never"))}
# #Error in if (options$noisey == TRUE) message(paste("\n", options$engine,  : 
#   argumento tiene longitud cero
# Calls: <Anonymous> ... sew.list -> lapply -> FUN -> sew.character -> <Anonymous>

#easystats::install_suggested()

options(scipen=2) #display numbers rather scientific number

#remotes::install_github("chjackson/flexsurv-dev", upgrade = "never")
#devtools::install_github("hputter/mstate", upgrade = "never")

#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:

fitstats.flexsurvreg = function(x){
  ll = x$loglik
  aic = x$AIC
  k = length(x$coefficients)
  n = sum(x$data$m["(weights)"])
  aicc = aic + ((2 * k) * (k + 1) / (n - k - 1))
  bic = - 2 * ll + (k * log(n))
  data.frame(
   Df = k,
    "n2ll" = -2 * ll,
    AIC = aic,
    AICc = aicc,
    BIC = bic
  )
}
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:


if(.Platform$OS.type == "windows") withAutoprint({
  memory.size()
  memory.size(TRUE)
  memory.limit()
})
memory.limit(size=56000)

path<-dirname(rstudioapi::getSourceEditorContext()$path)

options(knitr.kable.NA = '')

#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:
#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:#:

#to format rows in bold
format_cells <- function(df, rows ,cols, value = c("italics", "bold", "strikethrough")){

  # select the correct markup
  # one * for italics, two ** for bold
  map <- setNames(c("*", "**", "~~"), c("italics", "bold", "strikethrough"))
  markup <- map[value]  

  for (r in rows){
    for(c in cols){

      # Make sure values are not factors
      df[[c]] <- as.character( df[[c]])

      # Update formatting
      df[r, c] <- ifelse(nchar(df[r, c])==0,"",paste0(markup, gsub(" ", "", df[r, c]), markup))
    }
  }

  return(df)
}
#To produce line breaks in messages and warnings
knitr::knit_hooks$set(
   error = function(x, options) {
     paste('\n\n<div class="alert alert-danger">',
           gsub('##', '\n', gsub('^##\ Error', '**Error**', x)),
           '</div>', sep = '\n')
   },
   warning = function(x, options) {
     paste('\n\n<div class="alert alert-warning">',
           gsub('##', '\n', gsub('^##\ Warning:', '**Warning**', x)),
           '</div>', sep = '\n')
   },
   message = function(x, options) {
     paste('<div class="message">',
           gsub('##', '\n', x),
           '</div>', sep = '\n')
   }
)

 
irrs<-function(x, y="event", z="person_days",db){
  #x= variable que agrupa
  #y= evento explicado
  #z= person days
  #db= base de datos
  fmla <- as.formula(paste0(y,"~",x))
  fmla2 <- as.formula(paste0(z,"~",x))
assign(paste0("irr_",y,"_por_",x),
       rateratio.test::rateratio.test(
     x=as.numeric(xtabs(fmla, data=get(db)))[c(2,1)],
     n=as.numeric(xtabs(fmla, data=get(db)))[c(2,1)]
    )
   )
return(
  rateratio.test::rateratio.test(
     x=as.numeric(xtabs(fmla, data=get(db)))[c(2,1)],
     n=as.numeric(xtabs(fmla2, data=get(db)))[c(2,1)]
      )
    )
}
```

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      tidy = FALSE,
                      message = FALSE,
                      fig.align = 'center',
                      out.width = "100%")
options(knitr.table.format = "html") 
```


```{r, load_refs, include=F, cache=FALSE}
library(RefManageR)
BibOptions(check.entries = FALSE,
           bib.style = "numeric",
           cite.style = "numeric",
           style = "markdown",
           super = TRUE,
           hyperlink = FALSE,
           dashed = FALSE)

myBib <- ReadBib("_bibs/libreria_generica.txt", check = F,  .Encoding="latin1")
```

# Background

Research has shown that reducing SUDs through effective treatment leads to a reduction in criminal activity$`r Cite(myBib, c("prendergast2006"))`$. However, most evidence comes from developed countries, and results from the Latin American context are largely unknown$`r Cite(myBib, c("klingemann2020"))`$. The social, cultural, economic, epidemiological context and substance use treatment (SUT) policy response are different in this region, making the question about SUT effectiveness through locally based data relevant$`r Cite(myBib, c("Mateo_Pinones2022"))`$. 

We analyze Chile as a case study and examine the impact of SUT on the prevention of contact with the criminal justice system (CJS) in the short (1 year), middle (3 years) and long term (5 years). 
**Hypothesis:** Patients who complete treatment have lower probabilities of being in contact with CJS compared to patients who do not complete, although this effect may decrease as observation time passes.

# Methods

This research relies on a population-based record-linkage retrospective cohort design. We used a deterministic linkage process (using encryption of the Chilean Unique National ID) to merge electronic records of individuals in publicly funded Chilean SUT programs with the Prosecutor’s Office data at the national level between 2010 and 2019. This research is approved by the Griffith University Human Research Ethics Committee (GUHREC) (GU Ref No: 2022/919).
We described the cumulative incidence rate and incidence rate ratio (IRR) of contact with the CJS (offenses that ended with a condemnatory sentence and of offenses that ended with imprisonment after baseline treatment outcome), and its variation by baseline treatment outcome: Treatment completion, Late (>= 3months) & Early dropout (within the first 3 months of treatment). 
We calculated the association between Baseline treatment outcome and Contact with CJS through Royston-Parmar models while adjusting for several covariates and obtained standardized survival curves and restricted mean survival times (RMST) through the `stpm2` command in Stata$`r Cite(myBib, c("s457128"))`$. Missing data was imputed using multiple imputation with regression trees from `missRanger` R package$`r Cite(myBib, c("missranger"))`$. Secondary analyses included e-values of the strength of confounding needed to take away the associations between treatment outcome and contact with CJS. Codes are available at bit.ly/40cMATs. 
Covariates are listed below:

<ule>
  <li>Treatment setting</li>
  <li>Sex</li>
  <li>Substance use onset age</li>
  <li>Educational attainment</li>
  <li>Primary substance at admission</li>
  <li>Primary substance at admission usage frequency</li>
  <li>Occupational status</li>
  <li>Poly-substance use</li>
  <li>Number of children (binary)</li>
  <li>Tenure status of households</li>
  <li>Macrozone</li>
  <li>Number of previous offenses (violent)</li>
  <li>Number of previous offenses (acquisitive)</li>
  <li>Number of previous offenses (substance-related)</li>
  <li>Number of previous offenses (other)</li>
  <li>Psychiatric comorbidity (ICD-10)</li>
  <li>Substance use severity (dependence status) (ICD-10)</li>
  <li>Urban/rural municipality of residence</li>
  <li>Percentage of poverty of the municipality of residence</li>
  <li>Initial substance</li>
  <li>Birth year</li>
  <li>Cohabitation status</li>
  <li>Physical comorbidity</li>
  <li>Admission Age</li>
</ule>

<br>

<br>

# Preliminary Results

Of the `r format(nrow(CONS_C1_df_dup_SEP_2020), big.mark=",")`(p= `r format(length(unique(CONS_C1_df_dup_SEP_2020$hash_key)), big.mark=",")`) SENDA records of admissions,  `r format(nrow(Base_fiscalia_v14), big.mark=",")`(`r scales::percent(nrow(Base_fiscalia_v13)/length(unique(CONS_C1_df_dup_SEP_2020$hash_key)))`) were eligible to be matched with the Prossecutor's Office database (discarded ongoing treatments or treatments that ended in referrals). `r format(nrow(dplyr::filter(Base_fiscalia_v14, !is.na(dateofbirth_imp))), big.mark=",")`(`r scales::percent(nrow(dplyr::filter(Base_fiscalia_v14, !is.na(dateofbirth_imp)))/nrow(Base_fiscalia_v14))`) had at least an offense that ended with a condemnatory sentence after baseline treatment. Those that had at least an offense that ended with imprisonment were `r format(nrow(dplyr::filter(Base_fiscalia_v14_pris, !is.na(dateofbirth_imp))), big.mark=",")`(`r scales::percent(nrow(dplyr::filter(Base_fiscalia_v14_pris, !is.na(dateofbirth_imp)))/nrow(Base_fiscalia_v14_pris))`).

```{r exp-surv1, eval=T, echo=F, error=T, fig.align='center', message=FALSE, warning=FALSE, results='hide'}
library(tidyverse)
dplyr::bind_rows(
data.table::data.table(biostat3::survRate(Surv((age_offending_imp- edad_al_egres_imp), !is.na(dateofbirth_imp)) ~ motivodeegreso_mod_imp_rec, data= dplyr::filter(Base_fiscalia_v14,age_offending_imp- edad_al_egres_imp>=0))  %>% select(-1) %>%  dplyr::mutate_at(c("rate", "lower", "upper"),~round(.*1000,0)), keep.rownames=T),
data.table::data.table(biostat3::survRate(Surv((age_offending_imp- edad_al_egres_imp), !is.na(dateofbirth_imp)) ~ 1, data= dplyr::filter(Base_fiscalia_v14,age_offending_imp- edad_al_egres_imp>=0))  %>% dplyr::mutate_at(c("rate", "lower", "upper"),~round(.*1000,0)), keep.rownames = T) %>% dplyr::mutate(rn="Total"))%>% 
  as.data.frame() %>% 
  dplyr::mutate(rn= dplyr::case_when(grepl("Treatment completion",rn)~"Tr. Comp",grepl("Early",rn)~"Early Dis",grepl("Late",rn)~"Late Dis", T~"Total")) %>% 
  dplyr::mutate(tstop= round(tstop, 0)) %>% 
  format_cells(4, 1:length(names(.)), "bold") %>%
  knitr::kable("markdown", size=3, col.names= c("Outcome", "Person-time","Event", "Rate", "LoCI95%", "UpCI95%"), caption= "Offending with condemnatory sentence from Baseline Treatment Outcome (x1000 person-years)")
```

```{r exp-surv2, eval=T, echo=F, error=T, fig.align='center', message=FALSE, warning=FALSE}
Base_fiscalia_v14_comp<-
Base_fiscalia_v14 %>% 
  dplyr::mutate(mot_egres_latewdl=dplyr::case_when(grepl("Late",motivodeegreso_mod_imp)~"1.Late WDRL",
                                                        grepl("Therap",motivodeegreso_mod_imp)~"0.Therapeutic Disch.",TRUE~NA_character_)) %>% 
  dplyr::mutate(mot_egres_latewdl= factor(mot_egres_latewdl)) %>% 
  dplyr::mutate(mot_egres_earlywdl=dplyr::case_when(grepl("Early",motivodeegreso_mod_imp)~"1.Early WDRL",
                                                        grepl("Therap",motivodeegreso_mod_imp)~"0.Therapeutic Disch.",TRUE~NA_character_)) %>% 
  dplyr::mutate(mot_egres_earlywdl= as.factor(mot_egres_earlywdl)) %>% 
  dplyr::mutate(mot_egres_earlywdl_late=dplyr::case_when(grepl("Early",motivodeegreso_mod_imp)~"1.Early WDRL",
                                                        grepl("Late",motivodeegreso_mod_imp)~"0.Late WDRL",TRUE~NA_character_)) %>% 
  dplyr::mutate(mot_egres_earlywdl_late= as.factor(mot_egres_earlywdl_late)) %>% 
  dplyr::mutate(event= ifelse(!is.na(dateofbirth_imp),1,0)) %>% 
  dplyr::mutate(timetoevent= age_offending_imp- edad_al_egres_imp) %>% 
  ungroup()
Base_fiscalia_v14_pris_comp<-
Base_fiscalia_v14_pris %>% 
  dplyr::mutate(mot_egres_latewdl=dplyr::case_when(grepl("Late",motivodeegreso_mod_imp)~"1.Late WDRL",
                                                        grepl("Therap",motivodeegreso_mod_imp)~"0.Therapeutic Disch.",TRUE~NA_character_)) %>% 
  dplyr::mutate(mot_egres_latewdl= factor(mot_egres_latewdl)) %>% 
  dplyr::mutate(mot_egres_earlywdl=dplyr::case_when(grepl("Early",motivodeegreso_mod_imp)~"1.Early WDRL",
                                                        grepl("Therap",motivodeegreso_mod_imp)~"0.Therapeutic Disch.",TRUE~NA_character_)) %>% 
  dplyr::mutate(mot_egres_earlywdl= as.factor(mot_egres_earlywdl)) %>% 
  dplyr::mutate(mot_egres_earlywdl_late=dplyr::case_when(grepl("Early",motivodeegreso_mod_imp)~"1.Early WDRL",
                                                        grepl("Late",motivodeegreso_mod_imp)~"0.Late WDRL",TRUE~NA_character_)) %>% 
  dplyr::mutate(mot_egres_earlywdl_late= as.factor(mot_egres_earlywdl_late)) %>% 
  dplyr::mutate(event= ifelse(!is.na(dateofbirth_imp),1,0)) %>% 
  dplyr::mutate(timetoevent= age_offending_imp- edad_al_egres_imp) %>% 
  ungroup()

irrs_early_drop<-irrs(x="mot_egres_earlywdl", z="timetoevent", y="event", db="Base_fiscalia_v14_comp")
irrs_early_drop_pris<-irrs(x="mot_egres_earlywdl", z="timetoevent", y="event", db="Base_fiscalia_v14_pris_comp")
irrs_early_late_drop<-irrs(x="mot_egres_earlywdl_late", z="timetoevent", y="event", db="Base_fiscalia_v14_comp")
irrs_early_late_drop_pris<-irrs(x="mot_egres_earlywdl_late", z="timetoevent", y="event", db="Base_fiscalia_v14_pris_comp")
irrs_late_drop<-irrs(x="mot_egres_latewdl", z="timetoevent", y="event", db="Base_fiscalia_v14_comp")
irrs_late_drop_pris<-irrs(x="mot_egres_latewdl", z="timetoevent", y="event", db="Base_fiscalia_v14_pris_comp")
```

-	Compared to those receiving almost no treatment (early dropout), those completing SUT took longer to an offense leading to condemnatory sentence (IRR [Incidence rate ratio]= `r sprintf("%1.2f", irrs_early_drop$estimate[1])` 95% CI `r sprintf("%1.2f", irrs_early_drop$conf.int[1])`,`r sprintf("%1.2f", irrs_early_drop$conf.int[2])`; aHR[adjusted hazard ratio]: 1.74  95%CI 1.66, 1.83) and to an offense leading to imprisonment `r sprintf("%1.2f", irrs_early_drop_pris$estimate[1])` (95% CI `r sprintf("%1.2f", irrs_early_drop_pris$conf.int[1])`,`r sprintf("%1.2f", irrs_early_drop_pris$conf.int[2])`; aHR= 1.99 95%CI 1.79, 2.22).
-	Compared to receiving some treatment (late dropout), those completing SUT took longer (IRR= `r sprintf("%1.2f", irrs_late_drop$estimate[1])` 95% CI  `r sprintf("%1.2f", irrs_late_drop$conf.int[1])`,`r sprintf("%1.2f", irrs_late_drop$conf.int[2])`; aHR=1.58 95%CI 1.52, 1.65) to condemnatory sentence and to imprisonment (IRR= `r sprintf("%1.2f", irrs_late_drop_pris$estimate[1])` 95% CI  `r sprintf("%1.2f", irrs_late_drop_pris$conf.int[1])`,`r sprintf("%1.2f", irrs_late_drop_pris$conf.int[2])`; aHR=1.65 95%CI 1.51, 1.81). 
-	However, the difference was lower when we compared those who received some treatment (late dropout) with those with almost no treatment (early dropout) regarding the time to condemnatory sentence (IRR= `r sprintf("%1.2f", irrs_early_late_drop$estimate[1])` 95% CI `r sprintf("%1.2f", irrs_early_late_drop$conf.int[1])`,`r sprintf("%1.2f", irrs_early_late_drop$conf.int[2])`) and imprisonment (IRR= `r sprintf("%1.2f", irrs_early_late_drop_pris$estimate[1])` 95% CI  `r sprintf("%1.2f", irrs_early_late_drop_pris$conf.int[1])`,`r sprintf("%1.2f", irrs_early_late_drop_pris$conf.int[2])`). Differences between Early vs Late dropout did not overlap the null in Tables 1 & 2.

```{r exp-surv2-2, eval=T, echo=F, error=T, fig.align='center', message=FALSE, warning=FALSE, results='hide'}
dplyr::bind_rows(
data.table::data.table(biostat3::survRate(Surv((age_offending_imp- edad_al_egres_imp), !is.na(dateofbirth_imp)) ~ motivodeegreso_mod_imp_rec, data= dplyr::filter(Base_fiscalia_v14_pris,age_offending_imp- edad_al_egres_imp>=0))  %>% select(-1) %>%  dplyr::mutate_at(c("rate", "lower", "upper"),~round(.*1000,0)), keep.rownames=T),
data.table::data.table(biostat3::survRate(Surv((age_offending_imp- edad_al_egres_imp), !is.na(dateofbirth_imp)) ~ 1, data= dplyr::filter(Base_fiscalia_v14_pris,age_offending_imp- edad_al_egres_imp>=0))  %>% dplyr::mutate_at(c("rate", "lower", "upper"),~round(.*1000,0)), keep.rownames = T) %>% dplyr::mutate(rn="Total"))%>% 
  as.data.frame() %>% 
  dplyr::mutate(rn= dplyr::case_when(grepl("Treatment completion",rn)~"Tr. Comp",grepl("Early",rn)~"Early Dis",grepl("Late",rn)~"Late Dis", T~"Total")) %>% 
  dplyr::mutate(tstop= round(tstop, 0)) %>% 
  format_cells(4, 1:length(names(.)), "bold") %>%
  knitr::kable("markdown", size=3, col.names= c("Outcome", "Person-time","Event", "Rate", "LoCI95%", "UpCI95%"), caption= "Offending with imprisonment from Baseline Treatment Outcome (x1000 person-years)")
```

```{r exp-surv23-1, eval=T, echo=F, error=T, fig.align='center', message=FALSE, warning=FALSE}
require(XML); require(RCurl); require(rlist)
prob_imp<-rvest::read_html("prob_condsent_m1_main_alt.html") %>% rvest::html_table()
rmst_imp<-rvest::read_html("rmst_condsent_m1_main_alt.html") %>% rvest::html_table()
prob_imp_diff<-rvest::read_html("prob_condsent_m1_main_diff_alt.html") %>% rvest::html_table()
rmst_imp_diff<-rvest::read_html("rmst_condsent_m1_main_diff_alt.html") %>% rvest::html_table()

prob_imp_tab<-
prob_imp %>% as.data.table() %>% janitor::row_to_names(3) %>% 
  dplyr::rename("Time" = 1) %>% slice(2:4) %>% mutate(Comp_ci= paste0(Comp," (", Comp_lci,",",Comp_uci,")"), Early_ci = paste0(Early," (", Early_lci,",",Early_uci,")"), Late_ci = paste0(Late," (", Late_lci,",",Late_uci,")")) %>% 
  dplyr::select(Time, Comp_ci, Late_ci, Early_ci) %>% 
  dplyr::filter(!Time %in% c("3_mths","6_mths"))

prob_imp_diff_pris_tab<-
prob_imp_diff %>%  as.data.table() %>% janitor::row_to_names(3) %>% data.frame() %>% 
  dplyr::mutate_at(2:ncol(.), ~sprintf("%1.1f",readr::parse_number(.))) %>%
  dplyr::rename("Time" = 1) %>% slice(2:4) %>% 
    mutate(
    Comp_Early_ci= paste0(Comp.vs.Early," (", Comp.vs.Early.lci.,",",Comp.vs.Early.uci.,")"), 
    Comp_Late_ci = paste0(Comp.vs.Late," (", Comp.vs.Late..lci.,",",Comp.vs.Late..uci.,")"), 
    Early_Late_ci = paste0(Early.vs.Late," (", Early.vs.Late..lci.,",",Early.vs.Late..uci.,")")
  ) %>% 
  dplyr::select(Time, Comp_Late_ci, Comp_Early_ci, Early_Late_ci)

rmst_imp_tab<-
rmst_imp %>% as.data.table() %>% janitor::row_to_names(3) %>% data.frame() %>% 
  dplyr::mutate_at(2:ncol(.), ~sprintf("%1.3f",readr::parse_number(.))) %>% 
  dplyr::rename("Time" = 1) %>% slice(2:4) %>% 
  mutate(Comp_ci= paste0(Comp," (", Comp_lci,",",Comp_uci,")"), Early_ci = paste0(Early," (", Early_lci,",",Early_uci,")"), Late_ci = paste0(Late," (", Late_lci,",",Late_uci,")")) %>% 
  dplyr::select(Time, Comp_ci, Late_ci, Early_ci) 

rmst_imp_diff_tab<-
rmst_imp_diff %>% as.data.table() %>% janitor::row_to_names(3) %>% data.frame() %>% 
  dplyr::mutate_at(2:ncol(.), ~sprintf("%1.3f",readr::parse_number(.))) %>% 
  dplyr::rename("Time" = 1) %>% slice(2:4) %>% 
    mutate(
    Comp_Early_ci= paste0(Comp.vs.Early," (", Comp.vs.Early.lci.,",",Comp.vs.Early.uci.,")"), 
    Comp_Late_ci = paste0(Comp.vs.Late," (", Comp.vs.Late..lci.,",",Comp.vs.Late..uci.,")"), 
    Early_Late_ci = paste0(Early.vs.Late," (", Early.vs.Late..lci.,",",Early.vs.Late..uci.,")")
  ) %>% 
  dplyr::select(Time, Comp_Late_ci, Comp_Early_ci, Early_Late_ci)

rbindlist(list(list(c("Probs.",rep("",6))),cbind.data.frame(prob_imp_tab,prob_imp_diff_tab[,-1]), list(c("RMST",rep("",6))), cbind.data.frame(rmst_imp_tab,rmst_imp_diff_tab[,-1])), fill=T) %>% 
    dplyr::filter(nchar(Time)>=2) %>% #rio::export("_tab_mariel_results_cond_sent.xlsx")
  #knitr::kable("markdown", size=3, col.names= c("Time", "Complete Tr.","Late Disch.", "Early Disch.", "Comp. vs Late", "Comp. vs Early", "Early vs Late"), caption= "Offending with Condemnatory Sentence")
kbl(format = 'html',
        escape = FALSE,
        col.names= c("Time", "Complete Tr.","Late Disch.", "Early Disch.", "Comp. vs Late", "Comp. vs Early", "Early vs Late"), 
    caption= "Offending with Condemnatory Sentence") %>% 
    kable_styling(font_size = 22) %>%
    gsub("font-size: initial !important;", 
         "font-size: 27pt !important;", 
         .)
```

<br>

```{r exp-surv23-2, eval=T, echo=F, error=T, fig.align='center', message=FALSE, warning=FALSE}

prob_imp_pris<-rvest::read_html("prob_prison_m1_main_alt.html") %>% rvest::html_table()
rmst_imp_pris<-rvest::read_html("rmst_prison_m1_main_alt.html") %>% rvest::html_table()
prob_imp_diff_pris<-rvest::read_html("prob_prison_m1_main_diff_alt.html") %>% rvest::html_table()
rmst_imp_diff_pris<-rvest::read_html("rmst_prison_m1_main_diff_alt.html") %>% rvest::html_table()

prob_imp_pris_tab<-
prob_imp_pris %>% as.data.table() %>% janitor::row_to_names(3) %>% data.frame() %>% 
  dplyr::mutate_at(2:ncol(.), ~sprintf("%1.1f",readr::parse_number(.))) %>% 
  dplyr::rename("Time" = 1) %>% slice(2:4) %>% mutate(Comp_ci= paste0(Comp," (", Comp_lci,",",Comp_uci,")"), Early_ci = paste0(Early," (", Early_lci,",",Early_uci,")"), Late_ci = paste0(Late," (", Late_lci,",",Late_uci,")")) %>% 
  dplyr::select(Time, Comp_ci, Late_ci, Early_ci) 

prob_imp_diff_pris_tab<-
prob_imp_diff_pris %>% as.data.table() %>% janitor::row_to_names(3) %>% data.frame() %>% 
  dplyr::mutate_at(2:ncol(.), ~sprintf("%1.1f",readr::parse_number(.))) %>%
  dplyr::rename("Time" = 1) %>% slice(2:4) %>% 
    mutate(
    Comp_Early_ci= paste0(Comp.vs.Early," (", Comp.vs.Early.lci.,",",Comp.vs.Early.uci.,")"), 
    Comp_Late_ci = paste0(Comp.vs.Late," (", Comp.vs.Late..lci.,",",Comp.vs.Late..uci.,")"), 
    Early_Late_ci = paste0(Early.vs.Late," (", Early.vs.Late..lci.,",",Early.vs.Late..uci.,")")
  ) %>% 
  dplyr::select(Time, Comp_Late_ci, Comp_Early_ci, Early_Late_ci)

rmst_imp_pris_tab<-
rmst_imp_pris %>% as.data.table() %>% janitor::row_to_names(3) %>% data.frame() %>% 
  dplyr::mutate_at(2:ncol(.), ~sprintf("%1.3f",readr::parse_number(.))) %>% 
  dplyr::rename("Time" = 1) %>% slice(2:4) %>% 
  mutate(Comp_ci= paste0(Comp," (", Comp_lci,",",Comp_uci,")"), Early_ci = paste0(Early," (", Early_lci,",",Early_uci,")"), Late_ci = paste0(Late," (", Late_lci,",",Late_uci,")")) %>% 
  dplyr::select(Time, Comp_ci, Late_ci, Early_ci) 

rmst_imp_diff_pris_tab<-
rmst_imp_diff_pris %>% as.data.table() %>% janitor::row_to_names(3) %>% data.frame() %>% 
  dplyr::mutate_at(2:ncol(.), ~sprintf("%1.3f",readr::parse_number(.))) %>% 
  dplyr::rename("Time" = 1) %>% slice(2:4) %>% 
    mutate(
    Comp_Early_ci= paste0(Comp.vs.Early," (", Comp.vs.Early.lci.,",",Comp.vs.Early.uci.,")"), 
    Comp_Late_ci = paste0(Comp.vs.Late," (", Comp.vs.Late..lci.,",",Comp.vs.Late..uci.,")"), 
    Early_Late_ci = paste0(Early.vs.Late," (", Early.vs.Late..lci.,",",Early.vs.Late..uci.,")")
  ) %>% 
  dplyr::select(Time, Comp_Late_ci, Comp_Early_ci, Early_Late_ci)

rbindlist(list(list(c("Probs.",rep("",6))),cbind.data.frame(prob_imp_pris_tab,prob_imp_diff_pris_tab[,-1]), list(c("RMST",rep("",6))), cbind.data.frame(rmst_imp_pris_tab,rmst_imp_diff_pris_tab[,-1])), fill=T) %>% 
    dplyr::filter(nchar(Time)>=2) %>% # %>% rio::export("_tab_mariel_results.xlsx")
kbl(format = 'html',
        escape = FALSE,
        col.names= c("Time", "Complete Tr.","Late Disch.", "Early Disch.", "Comp. vs Late", "Comp. vs Early", "Early vs Late"), 
    caption= "Offending with imprisonment") %>% 
    kable_styling(font_size = 22) %>%
    gsub("font-size: initial !important;", 
         "font-size: 27pt !important;", 
         .)
```

- **Condemnatory Sentence**: E-value of at least 2.19 for Early and  2.01 for Late dropout vs. treatment completion.
- **Imprisonment**: E-value of at least 2.36 for Early and  1.99 for Late dropout vs. treatment completion.

The following figure depicts the predicted differences in survival probabilities and RMSTs for committing an offense that results in a condemnatory sentence and imprisonment.

```{r exp-surv3-prob-plot, eval=T, fig.align='center', message=F, echo=F, error=T, fig.align='center', fig.cap="", fig.retina=2, fig.cap="Differences in survival probabilities(left) and RMSTs(right) for time-to-condemnatory sentence(up) & imprisonment(bottom)"}
require(cowplot)
require(gridExtra)
require(coin)
require(magick)
fig1 <- image_read_svg('h_m_ns_rp6_stdif_s2_m1.svg')%>%
  image_annotate("A", 
                 location = "+0+0", 
                 size = 50, 
                 gravity = "northwest", 
                 boxcolor = "transparent", 
                 font = "Arial", 
                 strokecolor = "black", 
                 fill = "black")

fig2 <- image_read_svg('h_m_ns_rp6_stdif_rmst_m1.svg')
fig3 <- image_read_svg('h_m_ns_rp6_stdif_s2_pris_m1.svg')
fig4 <- image_read_svg('h_m_ns_rp6_stdif_rmst_pris_m1.svg')
#https://fondecytacc.github.io/nDP/analisis_mariel_feb_2023_stata_m1.html
#https://fondecytacc.github.io/nDP/analisis_mariel_feb_2023_stata_pris_m1.html
#ggsave(plot= p4,filename= "./_figs/SER2023_test.jpg", dpi=740, height = 16*0.7, width =20*0.7)
image_montage(c(fig1, fig2, fig3, fig4), tile = '2x2', geometry = 'x300+10+10',gravity = "Center")
```
```{r exp-surv3-rmst-plot, eval=T, fig.align='center', message=F, echo=F, error=T, eval=F, fig.align='center', fig.cap="", fig.retina=2, fig.cap="Differences in RMSTs for time-to-condemnatory sentence(left) & imprisonment(right)"}
image_montage(c(fig2, fig4), tile = '2x1', geometry = 'x300+10+10',gravity = "Center")
```

# Discussion

The greater the exposure of participants to Chilean treatment programs, the greater the effect on contacting the criminal justice system. Furthermore, the effect is consistent for any offense leading to a condemnatory sentence, including imprisonment, and remains significant after five years post-treatment. These findings are particularly relevant given the integrated approach to substance use treatment in Chile and other Latin American countries, where the effectiveness of such programs is unclear in a literature that typically focuses on specific approaches or substances and in short time periods$`r Cite(myBib, c("babor2021"))`$. This research acknowledges the constraints related to administrative data, such as hidden competing events and omitted variables bias (e.g., adolescent treatments). Regarding the generalizability of results, we recognize that the economic and social reality of Latin American countries can vary, even though findings might be more pertinent to these contexts than current evidence from developing countries.

# References

::: text_50_bib
```{r refs1, echo=FALSE, results="asis", warning=F}
suppressWarnings(PrintBibliography(myBib))
#https://github.com/ropensci/RefManageR/blob/master/R/rmdCite.R
```
:::

# Funding sources

::: text_60
- This work was funded by ANID - Millennium Science Initiative Program - N° NCS2021_003 (Castillo-Carniglia) and N° NCS2021_013 (Calvo); Authors have no conflict of interest to declare
- **Correspondence to**: Andrés González-Santa Cruz, gonzalez.santacruz.andres@gmail.com
:::